```{r configuration, echo=FALSE,message=FALSE,results='hide'}
##########################################
######     IPAQ PATH SHORT FORM  ##########
##########################################
rm(list=ls())
username<-'*******'  #add your own username #** 	#to change: will use getOption instead	
password<-'*******'  #add your own password  #** 	#to change: will use getOption instead	

###### CONNECT TO OPAL
library(opal)

url<-'https://cpt.maelstrom-research.org:444' #**
o<-opal.login(username, password, url)		

###SET WORKING and data DIRECTORY
workingDir<-'/home/your/working/dir/here'    #**
setwd(workingDir)

datasource<-'Atlantic_PATH'					#to change: will use getOption instead
table<-'Atlantic_PILOT_FINAL_copy'			#to change: will use getOption instead
datafile<-paste0(datasource, ".", table)
opal.assign(o,'DATA', datafile,missings=T)

require(gmodels)
#opal.execute(o,'require(gmodels)')  

# use graphics or not
withGraphs <-TRUE							#to change: will use getOption instead	
withGraphs & require(ggplot2) & opal.execute(o,'require(ggplot2)')
```

# Annexe: VALIDATION

## Exploratory Data analysis of `r table `

<br/>

### Module: Sociodemographic variables ##

#### Number of participants that have value <35 years for age calculated: 

`r opal.execute(o,'length(which(DATA$SDC_RECRUITMENT_AGE_CAL<35))') `

#### Number of participants that have value <70 years for age calculated:

`r opal.execute(o,'length(which(DATA$SDC_RECRUITMENT_AGE_CAL<70))') `

#### Number of participants that have value <35 years for age self-reported:

`r opal.execute(o,'length(which(DATA$SDC_RECRUITMENT_AGE_SR<35))') `

#### Number of participants that have value <70 years for age self-reported:

`r opal.execute(o,'length(which(DATA$SDC_RECRUITMENT_AGE_SR<70))') `

#### Number of participants where age calculed does not match age self-reported + or - 1 year:

`r opal.execute(o,'length(which((DATA$SDC_RECRUITMENT_AGE_CALC <  DATA$SDC_RECRUITMENT_AGE_SR - 1) | (DATA$SDC_RECRUITMENT_AGE_CALC > DATA$SDC_RECRUITMENT_AGE_SR + 1)))') `


### Module: Diabetes variables ##

<br/>

#### Consistency check with diabetes ever 

#### Table 1: DIS_DIAB_EVER * DIS_DIAB_TYPE

``` {r comment=NA,results='markup',echo=FALSE}

DIS_DIAB_EVER<-opal.execute(o,'DATA$DIS_DIAB_EVER')
DIS_DIAB_TYPE<-opal.execute(o,'DATA$DIS_DIAB_TYPE')

CrossTable(DIS_DIAB_EVER,DIS_DIAB_TYPE,digits=4,prop.r=T,prop.c=T,prop.t=F,prop.chisq=F,format='SPSS',missing.include=T)

```

<br/>

#### Table 2: DIS_DIAB_EVER * DIS_DIAB_ONSET

``` {r comment=NA,results='markup',echo=FALSE,message=FALSE,fig.height=11,fig.width=10}
DIS_DIAB_ONSET<-opal.execute(o,'DATA$DIS_DIAB_ONSET')
DIS_DIAB_ONSET<-as.factor(DIS_DIAB_ONSET)
#CrossTable(DIS_DIAB_ONSET,DIS_DIAB_EVER,digits=4,prop.r=T,prop.c=T,prop.t=F,prop.chisq=F,format='SPSS',missing.include=T)

ggplot()+geom_text(aes(DIS_DIAB_EVER,DIS_DIAB_ONSET,colour=DIS_DIAB_EVER,label=..count..),stat='bin',na.rm=T,parse=T)+guides(colour=FALSE)

```

<br/>

#### Consistency check Diabetes type with gender

#### Table 3: DIS_DIAB_TYPE * SDC_GENDER


``` {r comment=NA,results='markup',echo=FALSE}
SDC_GENDER<-opal.execute(o,'DATA$SDC_GENDER')

CrossTable(SDC_GENDER,DIS_DIAB_TYPE,digits=4,prop.r=T,prop.c=T,prop.t=F,prop.chisq=F,format='SPSS',missing.include=T)

```

<br/>

#### Number of participants where disease age of onset is greater than age calculated + 1 year

`r opal.execute(o,'length(which (DATA$DIS_DIAB_ONSET!=97 & DATA$DIS_DIAB_ONSET > DATA$SDC_RECRUITMENT_AGE_CALC + 1))') `

#### Statistics of age of onset for diabetes type I, diabetes type II  and diabetes type III:

``` {r comment=NA,results='markup',echo=FALSE}
DIS_DIAB_ONSET<-opal.execute(o,'DATA$DIS_DIAB_ONSET')
DIS_DIAB_TYPE<-opal.execute(o,'DATA$DIS_DIAB_TYPE')

ONSET_TYPE1<-DIS_DIAB_ONSET[which(DIS_DIAB_TYPE==1)]
ONSET_TYPE2<-DIS_DIAB_ONSET[which(DIS_DIAB_TYPE==2)]
ONSET_TYPE3<-DIS_DIAB_ONSET[which(DIS_DIAB_TYPE==3)]

ONSET_TYPE1[ONSET_TYPE1==97]<-NA
ONSET_TYPE2[ONSET_TYPE2==97]<-NA
ONSET_TYPE3[ONSET_TYPE3==97]<-NA

count1<-length(which(!is.na(ONSET_TYPE1)))
count2<-length(which(!is.na(ONSET_TYPE2)))
count3<-length(which(!is.na(ONSET_TYPE3)))

cat('-Summary statistics of Age of onset for diabetes type1')
summary1<-summary(ONSET_TYPE1)
summary1["Number"]<-count1
summary1

cat('-Summary statistics of Age of onset for diabetes type2')
summary2<-summary(ONSET_TYPE2)
summary2["Number"]<-count2
summary2

cat('-Summary statistics of Age of onset for diabetes type3')
summary3<-summary(ONSET_TYPE3)
summary3["Number"]<-count3
summary3

```

```{r diabetes_plot, echo=FALSE, fig.width=10, fig.height=11,eval=withGraphs,warning=FALSE,message=FALSE}
ggplot()+geom_text(aes(x=DIS_DIAB_TYPE,factor(DIS_DIAB_ONSET),color=DIS_DIAB_TYPE,label=..count..),stat='bin',na.rm=T,parse=T)+guides(color=FALSE)
```

### Module: Smoking variables

<br/>

#### Consistency check with smoking ever

#### Table 5: SMK_EVER * SMK_CIG_CUR_FREQ

``` {r comment=NA,results='markup',echo=FALSE}

SMK_EVER<-opal.execute(o,'DATA$SMK_EVER')
SMK_CIG_CUR_FREQ<-opal.execute(o,'DATA$SMK_CIG_CUR_FREQ')

CrossTable(SMK_EVER,SMK_CIG_CUR_FREQ,digits=4,prop.r=T,prop.c=T,prop.t=F,prop.chisq=F,format='SPSS',missing.include=T)

```

<br/>

#### Consistency check with daily smoker

#### Table 6: SMK_CIG_CUR_FREQ * SMK_CIG_DAILY_CUR_QTY_CAT

``` {r comment=NA,results='markup',echo=FALSE}

SMK_CIG_DAILY_CUR_QTY_CAT<-opal.execute(o,'DATA$SMK_CIG_DAILY_CUR_QTY_CAT')

CrossTable(SMK_CIG_DAILY_CUR_QTY_CAT,SMK_CIG_CUR_FREQ,digits=4,prop.r=T,prop.c=T,prop.t=F,prop.chisq=F,format='SPSS',missing.include=T)

```

<br/>

### Module IPAQ SITTING

```{r sitting_plot, echo=FALSE, fig.width=8, fig.height=5,eval=withGraphs}
PA_SIT_AVG_TIME_DAY<-opal.execute(o,'DATA$PA_SIT_AVG_TIME_DAY')
PA_TOTAL_SIT_TIME<-opal.execute(o,'DATA$PA_TOTAL_SIT_TIME')
ggplot()+scale_y_continuous()+scale_x_continuous()+geom_point(aes(PA_SIT_AVG_TIME_DAY,PA_TOTAL_SIT_TIME,colour=2),na.rm=T)+guides(colour=FALSE)

```

<br/>

### Module IPAQ SHORT FORM

```{r ipaq_short_plot,echo=FALSE,fig.width=12,fig.height=5,eval=withGraphs}

PA_LEVEL_SHORT<-opal.execute(o,'DATA$PA_LEVEL_SHORT')
PA_TOTAL_SHORT<-opal.execute(o,'DATA$PA_TOTAL_SHORT')
ggplot()+geom_text(aes(PA_TOTAL_SHORT,PA_LEVEL_SHORT,label=as.character(PA_LEVEL_SHORT),color=PA_LEVEL_SHORT),na.rm=T,size=4,)+guides(color=FALSE)

```



```{r clean-up, results='hide',echo=FALSE}
opal.logout(o)
```

<style type="text/css">
.navbar {
  display: none;
}

@media screen{
  h3 {
    border-top: solid 1px #ccc;
    padding-top: 12px;
  }
}


@media print{
  body {
    font-size: 12px;
  }
  h2, h3 {
    page-break-before: always;
  }
  .table{
    page-break-inside: avoid;
  }
} 

#toc {
  overflow: overlay;
  max-height: 500px;
}

.table {
  width: 0%;
}

.table td {
  min-width: 200px;
}

</style>
