```{r configuration, echo=FALSE,message=FALSE,results='hide'}
#
# Global settings
#
url <- getOption("opal.url","https://cpt.maelstrom-research.org:444")
username <- getOption("opal.username", "******") # add your own usrname
password <- getOption("opal.password", "******") # add your own password
datasource <- getOption("opal.datasource", "Atlantic_PATH")
table <- getOption("opal.table","Atlantic_PILOT_FINAL_copy")
withStatistics <- getOption("opal.withStatistics", TRUE)
withGraphs <- getOption("opal.withGraphs", TRUE)
withFullTable<-getOption("opal.withFullTable",TRUE)
```

```{r set-up, echo=FALSE,message=FALSE,results='hide'}
# set up dictionary and data
library(opal)
o <- opal.login(username, password, url)

if(withFullTable){
  variables <- opal.variables(o, datasource, table)  #<--- use for all variable in table (option1)

}else{
  #names of variables we need in the report  #<---only the name of variables are given (option2)
variables<-c('ADM_STUDY_ID','ADM_QX_VERSION','ADM_QX_LANGUAGE','ADM_QX_FORMAT','ADM_QX_COMPLETION','SDC_GENDER',
             'SDC_RECRUITMENT_AGE_CALC','SDC_RECRUITMENT_AGE_SR','DIS_DIAB_EVER','DIS_DIAB_TYPE','DIS_DIAB_ONSET',
             'SMK_EVER','SMK_CIG_CUR_FREQ','SMK_CIG_DAILY_CUR_QTY_CAT','PA_TOTAL_VIG_SHORT','PA_TOTAL_MOD_SHORT',
             'PA_TOTAL_WALK_SHORT','PA_TOTAL_SHORT','PA_LEVEL_SHORT','PA_TOTAL_VIG_LONG','PA_TOTAL_MOD_LONG',
             'PA_TOTAL_WALK_LONG','PA_TOTAL_LONG','PA_LEVEL_LONG','PA_SIT_AVG_TIME_WEEKDAY','PA_SIT_AVG_TIME_WEEKEND',
             'PA_SIT_AVG_TIME_DAY','PA_TOTAL_SIT_TIME')
}

t <- opal.table(o, datasource, table, counts=TRUE)
variableCount<-ifelse(class(variables)=='list',t$variableCount,length(variables))

if (withStatistics | withGraphs) {
  require(e1071)
  #opal.execute(o, 'require(e1071)')
  opal.assign(o,'D', paste0(datasource, ".", table),missings=T)
}
if (withGraphs) {
  require(ggplot2)
  opal.execute(o, 'require(ggplot2)')
}
```

# Harmonized dataset report for `r table`

<br/>

Name of the report     | Harmonized dataset report for `r table`
---------------------- | -------------------
Project                | `r datasource`
Table                  | `r table`
Number of variables    | `r variableCount`
Number of participants | `r t$valueSetCount`
Date                   | `r as.character(Sys.Date())`

## Variables

```{r variables, results='asis', echo=FALSE}
for (variable in variables) {
  
  if(withFullTable){
      cat(paste0("* [", variable$name, "](#", gsub("\\.","_",variable$name),")\n")) # use this when u call all the variables (option1)
  }else{
    cat(paste0("* [", variable, "](#", gsub("\\.","_",variable),")\n"))
  }
  
}
```

```{r run-variable-md, include=FALSE}
out <- NULL
for (variable in variables) {
  if(!withFullTable) variable<-opal.variable(o,datasource,table,variable)  #<-get variable in opal directly one by one when option2
  out <- c(out, knit_child('opal-variable.Rmd'), sep='\n')
}
```

`r paste(out, collapse='\n')`

```{r clean-up, results=FALSE,echo=FALSE}
opal.logout(o)
```

<style type="text/css">
@media print{
  body {
    font-size: 12px;
  }
  h2, h3 {
    page-break-before: always;
  }
  .table{
    page-break-inside: avoid;
  }
}  

@media screen{
  h3 {
    border-top: solid 1px #ccc;
    padding-top: 12px;
  }
}

.navbar {
  display: none;
}

#toc {
  overflow: overlay;
  max-height: 500px;
}

.table {
  width: 0%;
}

.table td {
  min-width: 200px;
}

</style>
