---
output:
  knitrBootstrap::knit_bootstrap:
    encoding: UTF-8
    input: "opal-table.Rmd"
    boot_style: flatly
    chooser: NULL
    thumbsize: 7
---
```{r setChunkOptions, echo=FALSE,include=FALSE}
library(knitr)
opts_chunk$set(strip.white=TRUE,fig.align='center',collapse=TRUE,fig.width=8, fig.height=5,message=FALSE,verbose=FALSE) 
```

```{r ext, echo=FALSE,message=FALSE,results='hide', cache=FALSE}
read_chunk('config.R')
```

```{r set-up, echo=FALSE,message=FALSE,results='hide'}
<<connection>>
<<configuration>>
# set up dictionary and data
library(opal)
o <- opal.login(username, password, url) #log info from 'config.R' 

if(withFullTable){
  variables <- opal.variables(o, datasource, table)  #<--- use for all variable in table (option1)

}else{
  #names of variables we need in the report  #<---only the name of variables are given (option2)
  <<variablelist>>
 }  
t <- opal.table(o, datasource, table, counts=TRUE)
variableCount<-ifelse(class(variables)=='list',t$variableCount,length(variables))

if (withStatistics | withGraphs) {
  library(e1071)
  opal.execute(o, 'require(e1071)')
  opal.assign(o,'D', paste0(datasource, ".", table),missings=T)
}
if (withGraphs) {
  library(ggplot2)
  opal.execute(o, 'require(ggplot2)')
}
```

# Harmonized dataset report for `r table`

<br/>

Name of the report     | Harmonized dataset report for `r table`
---------------------- | -------------------
Project                | `r datasource`
Table                  | `r table`
Number of variables    | `r variableCount`
Number of participants | `r t$valueSetCount`
Date                   | `r as.character(Sys.Date())`

## Variables

```{r variables, results='asis', echo=FALSE}
for (variable in variables) {
  
  if(withFullTable){
      cat(paste0("* [", variable$name, "](#", gsub("\\.","_",variable$name),")\n")) # use this when u call all the variables (option1)
  }else{
    cat(paste0("* [", variable, "](#", gsub("\\.","_",variable),")\n"))
  }
  
}
```

```{r run-variable-md, include=FALSE}
out <- NULL
for (variable in variables) {
  if(!withFullTable) variable<-opal.variable(o,datasource,table,variable)  #<-get variable in opal directly one by one when option2
  out <- c(out, knit_child('opal-variable.Rmd'), sep='\n')
}
```

`r paste(out, collapse='\n')`

```{r clean-up, results=FALSE,echo=FALSE}
opal.logout(o)
```

<style type="text/css">
@media print{
  body {
    font-size: 12px;
  }
  h2, h3 {
    page-break-before: always;
  }
  .table{
    page-break-inside: avoid;
  }
}  

@media screen{
  h3 {
    border-top: solid 1px #ccc;
    padding-top: 12px;
  }
}

.navbar {
  display: block;
}


#toc {
  overflow: overlay;
  max-height: 500px;
}
body h2, h3, h1, .knitr {
    color: black;
}

.table {
  width: 70%;
  color: black;
}

.table td {
  min-width: 50px;
}

</style>