#### Statistics
```{r,echo=FALSE}
value<-opal.execute(o,paste0("D$",variable$name))
```

```{r, echo=FALSE,eval=hasCategories & !hasNonMissingCategory}
for(category in variable$categories){
  if (category$isMissing){
    value[which(value==category$name)]<-NA
  }
}

```

Descriptive Statistic | Value
--------------------- | ----------------
N                     | `r length(which(!is.na(value)))`
Min                   | `r min(value,na.rm=T)`
Max                   | `r max(value,na.rm=T)`
Mean                  | `r mean(value,na.rm=T)`
Median                | `r median(value,na.rm=T)`
Standard Deviation    | `r sd(value,na.rm=T)`
Variance              | `r var(value,na.rm=T)`
Skewness              | `r skewness(value,na.rm=T)`
Kurtosis              | `r kurtosis(value,na.rm=T)`
Sum                   | `r sum(value,na.rm=T)`
Sum of squares        | `r sum(value^2,na.rm=T)`
Missing               | `r length(which(is.na(value)))`


```{r, echo=FALSE, eval=withGraphs, fig.width=6, fig.height=3}
# see http://docs.ggplot2.org/current/geom_histogram.html
#plot(opal.execute(o, paste0("hist(D$", variable$name,")")))
bin<-(max(value,na.rm=T)-min(value,na.rm=T))/20
#opal.execute(o, paste0("qplot(", value,",geom='histogram',binwidth=" ,bin, ",fill=I('lightblue3'),colour=I('yellow'),xlab=",variable$name,")"))
qplot(value,geom='histogram',xlab=variable$name,binwidth=bin,fill=I('lightblue3'),colour=I('yellow'))
```
